Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity

### 2015-10-23 Acknowledgements.tex
Many of Ricardo's comments were addressed.

 We express our appreciation to Art Frankel, PhD, of the U.S. Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package. We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters. We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog. We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.

>>>>

 We express our appreciation to Art Frankel, PhD, of the U.S. Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package. We are also very thankful to Andrzej Kijko, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters. We wish to thank Mehdi Zare, International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog. We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.

### 2015-10-23 Discussion.tex
Many of Ricardo's comments were addressed.

\begin{table}[h]
\centering
\caption{Comparison of PGA, from different studies for selected cities in Northern Iran. (V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}

>>>>

\begin{table}[h]
\centering
\caption{Comparison of PGA, from different studies for selected cities in Northern Iran. (V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012} , Ak2011: \citet{Akbari2011} ) }
\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}

### 2015-10-23 MH_calculation.tex
Many of Ricardo's comments were addressed.

To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}. In this model, seismic events are spatially gridded to cells. We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage. According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above. Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur. Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ . Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past. \\
\noindent
According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage. In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure. In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
\noindent
According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km). This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$. Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ). The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c. For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}

@@

\noindent
where,  $\tilde{n}_i$  is normalized to preserve the total number of events. $\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell. The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
\noindent
For a grid of sites and by using $\tilde{n}_i$ from Eq. (1), the annual probability of exceeding specified ground motions is calculated. For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site. Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:

\begin{equation}
\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
\end{equation}

\noindent
where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$. Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation. The $b-value$ is considered uniform throughout most of the area. $P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$. This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}

>>>>

To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}. In this model, seismic events are spatially gridded to cells. We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage. According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above. Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur. Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ . Category 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past. \\
\noindent
According to Building and Housing Research Center  \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage. In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure. In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation. \\
\noindent
\noindent
In order to calculate the annual rate ($\lambda$) of exceeding ground motion (u) at a specific site, according to \citet{Frankel1995}, first we need to divide the region into cells (0.1*0.1) and count all earthquake events which are bigger than $M_{ref}$ in each cell. We use Herrmann formula \citep{Herrmann1977} to convert the cumulative (i.e. number of events bigger than $M_{ref}$) values to incremental (i.e. number of events from$M_{ref}$ to $M_{ref}+\Delta_m$) values. Using Gaussian function we smooth the number of events in each cell. The smoothed value $\tilde{n}_i$ is obtained from

@@

\noindent
where,  $\tilde{n}_i$  is normalized to preserve the total number of events. $\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell. The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
\noindent
Then we discretized the magnitude and distance in uniform bins and get the total number of Normalized, smoothed events ($N_k$) inside the certain distance increment.
Having ($N_k$) and $T$ (catalog time duration that we calculated $N_k$ within that duration), we can calculate the annual rate  $\lambda (u> u_0 )$ of exceeding ground motion according to

\begin{equation}
\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
\end{equation}
\noindent
where $k$ and $l$ are denoted as index of distance and magnitude bin. $P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$. This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}

### 2015-10-23 abstract.tex
Many of Ricardo's comments were addressed.

In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs. We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity. In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells. We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes. We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them. We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude. For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3. To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively. Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.  We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran. The horizontal peak ground acceleration is selected as the ground motion parameter. The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions. The seismic hazard map for northern Iran is presented. The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region. The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.

>>>>

In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs. We evaluate seismic hazard over whole three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) and part of two tectonic seismic zones (Zagros and Central-East Iran) using smoothed historical seismicity. In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells. We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes. We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them. We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude. For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3. To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively. Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.  We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran. The horizontal peak ground acceleration is selected as the ground motion parameter. The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions. The seismic hazard map for northern Iran is presented. The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region. The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.

### 2015-10-23 completness_test.tex
Many of Ricardo's comments were addressed.

\section{Completeness tests}
For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor. To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.   Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.

@@

We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report. Table 1 presents the completeness of catalog of each region for different moment magnitudes.

>>>>

\section{Completeness tests}
For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor. In order to determine the catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.   Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness. Fig.~\ref{fig:comptest} (a,b,c) show the plot of earthquake magnitude with time. Fig.~\ref{fig:comptest}(d-o) present the cumulative number of earthquake with magnitude, in defined ranges. We define a completeness of each magnitude range at a time which the cumulative number of earthquake increase linearly with time. These times which presents the completeness of the catalog of each region for different moment magnitude are represented at Table 1. We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.

@@

### 2015-10-23 introduction.tex
Many of Ricardo's comments were addressed.

In this study we used smoothed seismicity \citep{Frankel1995}. We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh. We computed seismic parameters and catalog completeness in these regions. Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part. We used \citet{Karimiparidari2013} seismicity parameters in these regions.  We consider the MW5 earthquake as a threshold magnitude  for structural damage. In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.

@@

\section{Seismic regions and seismicity rate}
With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones. Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$). A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}. \citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog. The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities. 
In the present study, historical data are integrated with instrumental data. For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.

\subsection{Alborz Mountain Range (Alborz)}
Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt. Here a series of historical earthquakes occurred within a time period of more than 1100 years. Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region. At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression. An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.

\subsection{Azerbaijan}
There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest. The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus. The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF. Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7). However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them. Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.

\subsection{Kopeh Dagh}
The main Kopeh-Dagh fault system has experienced some historic earthquakes. Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran. This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs. The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}. \citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km. 
Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.

>>>>

In this study we used smoothed seismicity \citep{Frankel1995}. We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh. We also consider seismicity of part of Central-East Iran and Zagros regions. We computed seismic parameters and catalog completeness in these regions. Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part. We used \citet{Karimiparidari2013} seismicity parameters in these regions.  We consider the $Mw5$ earthquake as a threshold magnitude  for structural damage. In order to consider damage to the historical masonry building we also considered $Mw4.5$ as a threshold for structural damage to these kind of building.

@@

\section{Seismic regions and seismicity rate}
With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones. Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$). A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}. \citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog. The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities. 
In the present study, historical data are integrated with instrumental data. We use the tectonic seismic division to categorized the data according to the seismic tectonic regions. 
\subsection{Alborz Mountain Range (Alborz)}
Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt. Here a series of historical earthquakes occurred within a time period of more than 1100 years. Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region. At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran.
The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz.
The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression. An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.

\subsection{Azerbaijan}
There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest. The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus. The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF. Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879. Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7)\citep{Berberian1999}.

\subsection{Kopeh Dagh}
The main Kopeh-Dagh fault system has experienced some historic earthquakes. Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran. This was the strongest earthquake to strike this region since at least 1455.
The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs. The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}. \citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km. 
Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
